%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned,NoDate]{currvita} % Use the currvita style for the layout of the document
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top
\newcommand{\hll}[1]{{\color{Maroon}\textsc{#1}}}
\newcommand{\hlll}[1]{{\color{CadetBlue}\textsc{#1}}}

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

%\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
%\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\NewEntry}[2]{\noindent #1 #2 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.25em}} % Add some white space after each new entry

\newcommand{\IndentEntry}[3]{\raggedright\hangindent=2em\hangafter=0 \noindent {\footnotesize #1 {\sc \color{Maroon}#2} #3}
\vspace{0.25em}}

% Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field

\newcommand{\Description}[1]{\raggedright\footnotesize{#1}\par\normalsize\vspace{0.5em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Jonathan Chang}} % Your name

% \noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\begin{flushright}{\vspace{-2.75em}
{\href{mailto:slycoder@gmail.com}{slycoder@gmail.com}} \\
{+1 (310) 425 3759}
}\end{flushright}

%\vspace{1em} % Extra white space between the personal information section and goal
\vspace{-0.25em}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{0.5em}

\NewEntry{2014--Present, Sr.\ Data Scientist, \hll{Zipongo}}

\Description{Led efforts to collect, analyze, and leverage data for nearly every product across the company.}

\IndentEntry{}{Data engineering}{
Integrated with partners and clients to gather data to support products and
drive user engagement.  For example, integrated with food service providers to
collect information about recipes, restaurants, and groceries to be used in
a variety of products.  Built out integrations with tools such as email service
providers to allow for engaging email campaigns.  Drove the design and
implementation of a flexible survey system to gather data from users.  With so
much variegated data flowing through our system, I designed and built systems
for ETL and experimentation so that non-engineers can understand and visualize
usage trends while respecting the privacy of users' health data.}

\IndentEntry{}{Machine learning}{
Leveraged novel machine learning and natural language processing techniques to make
structured and unstructured predictions.  For example, made predictions about food
flavors, nutrition, etc.\ robust to varying levels of data quality.  Modeled
user health and nutrition by marrying techniques from the nutrition literature
with our proprietary data. Paired our understanding of food and nutrition to
build out scalable search and recommendation systems to improve user health.}

\NewEntry{2009--2014, Data Scientist, \hll{Facebook}}

\Description{Mined and analyzed data from a variety of sources. Applied large-scale machine learning techniques to solve prediction problems which power user-facing products. Developed tools and infrastructure to make data manipulation and analysis easier company-wide.}

\IndentEntry{2012--2014}{User Modeling Team}{
  Tech lead on efforts to improve and consolidate machine learning algorithms
  for predicting user attributes.  Work closely with both front-end and
  infrastructure teams to develop impactful predictions.
}

\IndentEntry{2010--2012}{Entities}{
  Founding member of the Entities team which manages structured data on
  Facebook. Helped develop techniques for entity extraction, deduplication,
  disambiguation, etc.  Worked on a number of classification problems such as
  authenticity.  Focused especially on building databases for music and places
  and was involved in the launch of those integrations on Facebook.
}

\IndentEntry{2009--2010}{Data Science Team}{
  Used novel statistical machine learning to analyze the Facebook user base.  Projects included inferring user
  ethnicity, analyzing intra- and inter-ethnic interactions, and predicting
  user engagement. Blog posts are available for some analyses (e.g., \href{http://on.fb.me/1qOHwiY}{http://on.fb.me/1qOHwiY}, \href{http://on.fb.me/1uqyxab}{http://on.fb.me/1uqyxab}, \href{http://on.fb.me/1BwWijc}{http://on.fb.me/1BwWijc}).
}

\NewEntry{2007, Intern, \hll{Google}}

\Description{Performed research on determining location relevance for the Books: Mapped project.}

%\NewEntry{2006}{Intern, \hll{INRIA}}

%\Description{Performed research in and developed novel modular simulation methodologies for simulating processor architectures.}

%\NewEntry{2002}{Intern, \hll{nVidia}}

%\Description{Hardware engineering intern.  Designed and tested portions of production graphics processor.}
%------------------------------------------------

\vspace{0.25em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{0.5em}

\NewEntry{2003--2009}{Doctor of Philosophy, \hll{Princeton University}}

\Description{GPA: 3.8\ \ $\cdotp$\ \ \textit{Machine learning}, Department of Electrical Engineering\newline
Thesis: \textit{Uncovering, Understanding, and Predicting Links}\newline
Advisor: Prof.~David \textsc{Blei}\newline
Released \texttt{lda} for R, a commonly used package for topic modeling.}

%------------------------------------------------

\NewEntry{1999--2003}{Bachelor of Science, \hll{California Institute of Technology}}

\Description{GPA: 3.8\ \ $\cdotp$\ \ \textit{Electrical and Computer Engineering with Honors}}

%------------------------------------------------

\vspace{0.25em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Selected Publications}\vspace{0.5em}

%------------------------------------------------

\NewEntry{\hlll{Location$^3$: How Users Share and Respond to Location-Based Data on Social Networking Sites}}

\Description{Jonathan Chang and Eric Sun.
\textit{Proceedings of the International Conference in Weblogs and Social Media (ICWSM), 2011.}}

\NewEntry{\hlll{Not-so-latent Dirichlet Allocation: Collapsed Gibbs Sampling Using Human Judgments}}

\Description{Jonathan Chang.
\textit{Proceedings of the NAACL HLT 2010 Workshop on Creating Speech and Language Data with Amazon's Mechanical Turk, 2010.}}

\NewEntry{\hlll{ePluribus: Ethnicity on Social Networks}}

\Description{Jonathan Chang, Itamar Rosenn, Lars Backstrom, and Cameron Marlow.
\textit{Proceedings of the International Conference in Weblogs and Social Media (ICWSM), 2010.}
\textbf{Winner Best Paper Award}}

\NewEntry{\hlll{Hierarchical Relational Models for Document Networks}}

\Description{Jonathan Chang and David M. Blei.
\textit{Annals of Applied Statistics, Volume 4, Number 1, 2010.}}

\NewEntry{\hlll{Reading Tea Leaves: How Humans Interpret Topic Models}}

\Description{Jonathan Chang, Jordan Boyd-Graber, Sean Gerrish, Chong Wang, and David M. Blei.
\textit{Advances in Neural Information Processing Systems, 2009.}
\textbf{Honorable Mention}}

\NewEntry{\hlll{Connections Between the Lines: Augmenting Social Networks with Text}}

\Description{Jonathan Chang, Jordan Boyd-Graber, and David M. Blei.
\textit{Proceedings of the 15th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, 2009.}}

\NewEntry{\hlll{Automatic Instruction-Level Software-Only Recovery Methods}}

\Description{Jonathan Chang, George A. Reis, and David I. August.
\textit{Proceedings of the International Conference on Dependable Systems and Networks, 2006.}
\textbf{Winner William C. Carter Award}}

\NewEntry{\hlll{SWIFT: Software Implemented Fault Tolerance}}

\Description{George A. Reis, Jonathan Chang, Neil Vachharajani, Ram Rangan, and David I. August.
\textit{Proceedings of the Third International Symposium on Code Generation and Optimization, 2005.}
\textbf{Winner Best Paper Award. Winner of the 2015 International Symposium on Code Generation and Optimization Test of Time Award.}}

\spacedlowsmallcaps{Other Publications}\vspace{0.5em}

\NewEntry{\hlll{Joint Inference of Multiple Label Types in Large Networks}}

\Description{Deepayan Chakrabarti, Stanislav Funiak, Jonathan Chang, Sofus Macskassy.
\textit{Proceedings of The 31st International Conference on Machine Learning, 2014.}}

\NewEntry{\hlll{Learning a concept hierarchy from multi-labeled documents}}

\Description{Viet-An Nguyen, Jordan L Boyd-Graber, Philip Resnik, Jonathan Chang.
\textit{Advances in Neural Information Processing Systems, 2014.}}

\NewEntry{\hlll{Tree-based label dependency topic models}}

\Description{Viet-An Nguyen, Jordan Boyd-Graber, Jonathan Chang, Philip Resnik.
\textit{NIPS Workshop on Topic Models: Computation, Application, and Evaluation, 2013.}}

\NewEntry{\hlll{Erratum: Sgdqn is less careful than expected}}

\Description{Antoine Bordes, Léon Bottou, Patrick Gallinari, Jonathan Chang, S Alex Smith.
\textit{The Journal of Machine Learning Research, Volume 11, 2010.}}

\NewEntry{\hlll{Mixtures of clusterings by boosting}}

\Description{Jonathan Chang, David M Blei.
\textit{Learning Workshop, 2009.}}

\NewEntry{\hlll{Relational topic models for document networks}}

\Description{Jonathan Chang, David M Blei.
\textit{International Conference on Artificial Intelligence and Statistics, 2009.}}

\NewEntry{\hlll{PU-BCD: exponential family models for the coarse-and fine-grained all-words tasks}}

\Description{Jonathan Chang, Miroslav Dudík, David M Blei.
\textit{Proceedings of the 4th International Workshop on Semantic Evaluations, 2007.}}

\NewEntry{\hlll{Unisim: An open simulation environment and library for complex architecture design and collaborative development}}

\Description{David August, Jonathan Chang, Sylvain Girbal, Daniel Gracia-Perez, Gilles Mouchard, David Penry, Olivier Temam, Neil Vachharajani.
\textit{Computer Architecture Letters, Volume 6, Number 2, 2007.}}

\NewEntry{\hlll{Automatic instruction-level software-only recovery}}

\Description{George A Reis, Jonathan Chang, David I August.
\textit{IEEE Micro, Volume 27, Number 1, 2007.}}

\NewEntry{\hlll{Non-uniform fault tolerance}}

\Description{Jonathan Chang, George A Reis, Neil Vachharajani, Ram Rangan, David August.
\textit{Proceedings of the 2nd Workshop on Architectural Reliability, 2006.}}

\NewEntry{\hlll{Selective runtime memory disambiguation in a dynamic binary translator}}

\Description{Bolei Guo, Youfeng Wu, Cheng Wang, Matthew J Bridges, Guilherme Ottoni, Neil Vachharajani, Jonathan Chang, David I August.
\textit{Compiler Construction, Pages 65--79, 2006.}}

\NewEntry{\hlll{Configurable transient fault detection via dynamic binary translation}}

\Description{George A Reis, Jonathan Chang, David I August, Robin Cohn, Shubhendu S Mukherjee.
\textit{Proceedings of the 2nd Workshop on Architectural Reliability, 2006.}}

\NewEntry{\hlll{Software-controlled fault tolerance}}

\Description{George A Reis, Jonathan Chang, Neil Vachharajani, Ram Rangan, David I August, Shubhendu S Mukherjee.
\textit{ACM Transactions on Architecture and Code Optimization, Volume 4, Number 2, 2005.}}

\NewEntry{\hlll{Design and evaluation of hybrid fault-detection systems}}

\Description{George Reis, Jonathan Chang, Neil Vachharajani, Shubhendu S Mukherjee, Ram Rangan, David August.
\textit{Proceedings of the 32nd International Symposium on Computer Architecture, 2005.}}

\NewEntry{\hlll{RIFLE: An architectural framework for user-centric information-flow security}}

\Description{Neil Vachharajani, Matthew J Bridges, Jonathan Chang, Ram Rangan, Guilherme Ottoni, Jason Blome, George Reis, Manish Vachharajani, David August.
\textit{Proceedings of the 37th International Symposium on Microarchitecture, 2004.}}

\NewEntry{\hlll{The Lutonium: A sub-nanojoule asynchronous 8051 microcontroller}}

\Description{Alain J Martin, Mika Nyström, Karl Papadantonakis, Paul Pénzes, Piyush Prakash, Catherine G Wong, Jonathan Chang, Kevin S Ko, Benjamin Lee, Elaine Ou, James Pugh, Eino-Ville Talvala, James T Tong, Ahmet Tura.
\textit{Proceedings of the Ninth International Symposium on Asynchronous Circuits and Systems, 2003.}}

%----------------------------------------------------------------------------------------
% \vspace{5.5em}
\spacedlowsmallcaps{Patents}\vspace{0.5em}

\NewEntry{\hlll{Methods and systems for inferring user attributes in a social networking system}}

\Description{Mitu Singh, Philip Bohannon, Jonathan Chang, Ismail Onur Filiz, Tudor Andrei Alexandrescu, Cameron Marlow.  \textit{Application \#US20140279722}}

\NewEntry{\hlll{Determining a Location and Area of a Place}}

\Description{Yuntao Jia, Mukund Narasimhan, Jonathan Chang, Joshua Redstone. \textit{Application \#US20140019532}}

\NewEntry{\hlll{Enabling preference portability for users of a social networking system}}

\Description{Robert William Cathcart, Rafael Linden Sagula, Cameron Alexander Marlow, Jonathan Chang, Siddharth Kar, Eric Sun. \textit{Application \#US20130124624}}

\NewEntry{\hlll{Providing universal social context for concepts in a social networking system}}

\Description{Robert William Cathcart, Rafael Linden Sagula, Cameron Alexander Marlow, Jonathan Chang, Siddharth Kar, Eric Sun. \textit{Application \#US20130124627}}

\NewEntry{\hlll{Searching topics by highest ranked page in a social networking system}}

\Description{Robert William Cathcart, Rafael Linden Sagula, Cameron Alexander Marlow, Jonathan Chang, Siddharth Kar, Eric Sun. \textit{Application \#US20130124626}}

\NewEntry{\hlll{Identifying relevant data for pages in a social networking system}}

\Description{Cameron Alexander Marlow, Robert William Cathcart, Jeffrey Scott Dunn, Rafael Linden Sagula, Venkataramanan Iyer Nandagopal, Siddharth Kar, Jonathan Chang.  \textbf{Granted \#US8935299}}

\NewEntry{\hlll{Determining a community page for a concept in a social networking system}}

\Description{Robert William Cathcart, Rafael Linden Sagula, Cameron Alexander Marlow, Jonathan Chang, Siddharth Kar, Eric Sun.  \textbf{Granted \#US8965970}}

\vspace{0.5em}
\spacedlowsmallcaps{Other Projects}\vspace{0.5em}

\NewEntry{\hlll{lda: Collapsed Gibbs sampling methods for topic models}}

\Description{I developed and continue to maintain a popular package for topic modeling in R.  The package contains a number of commonly used models and leverages collapsed Gibbs sampling for inference.  It is available at
\href{https://cran.r-project.org/web/packages/lda/}{https://cran.r-project.org/web/packages/lda/}.}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
